Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Remove todo about close neighbour
Fix terminology in extended origin

  This notion extends to sets of points. Since an there may be an infinite
  number of points, we measure the distance from the closest one.

  \todo{Mistral to check: I may have broken this notion}
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for an $N$-dimensional subscript $S$
  is denoted with $|S|$ and is defined as:
%
  \begin{align*}
    |S| & = \sum_{i=1}^{N} dist_i(S)
    &
    \textit{dist}_i(S) & = \begin{cases}
      0 & \pi_i(S) = \interv{-\infty}{\infty}{} \\
      |\mathsf{a}| - 1 & \pi_i(S) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  \todo{%
    Not sure what we are going to prove here? That it is a metric space or
    something?

@@

\todo{%
  We used to call the below property contiguity, and I think this is a natural
  notion- does ``close neighbour'' have some standard use or is it okay to call
  this contiguity?

  Response: how about adjecency?
}
\begin{defn}{(Adjacent)}
  A subscript $S$ is said to be \emph{adjacent at index $j$} of another
  subscript $S'$ if for every index $i$ except $j$, $\pi_i(S) = \pi_i(S')$ but
  at $j$ then $\pi_j(S) \neq \pi_i(S')$ such that $|S| = |S'| + 1$.

>>>>

  This notion extends to subscripts. Since there may be an infinite number of
  points, we measure the distance from the closest one.
\end{defn}
%
\begin{prop}{}
  The closed form of extend origin distance for an $N$-dimensional subscript $S$
  is denoted with $|S|$ and is defined as:
%
  \begin{align*}
    |S| & = \sum_{i=1}^{N} dist_i(S)
    &
    \textit{dist}_i(S) & = \begin{cases}
      0 & \pi_i(S) = \interv{-\infty}{\infty}{} \\
      |\mathsf{a}| - 1 & \pi_i(S) = \{\mathsf{a}\} \\
    \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
  \todo{%
    Not sure what we are going to prove here? That it is a metric space or
    something?

@@

\begin{defn}{(Adjacent)}
  A subscript $S$ is said to be \emph{adjacent at index $j$} of another
  subscript $S'$ if for every index $i$ except $j$, $\pi_i(S) = \pi_i(S')$ but
  at $j$ then $\pi_j(S) \neq \pi_i(S')$ such that $|S| = |S'| + 1$.
